\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-04-24 journalWallFriction/theory2robAlgs.tex
a lot of figures are corrected

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 hits the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(right) Similarly, if particle 2 hits the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
}
\end{figure}
If a particle is touching a wall, the other particle can move freely in the reachable set as shown in Fig.~\ref{fig:TwoRegions}.
 We compute the reachable set for any convex workspace.
 Fig.~\ref{fig:polygonAlg} illustrates the procedure to construct the reachable set generated by collisions with the $i^{th}$ side. If one particle hist side $i$ before the other ($\overline{\rm s_1s_2 }\nparallel \overline{\rm p_i p_{i+1}} $), the reachable set is defined by a polygon, constructed in line 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the reachable set of $\Delta$ configurations.
 % by computing the reachable set for all the sides of the polygon. Fig.~\ref{fig:polygonAlg} shows different cases with the particles and an arbitrary side. If particle 2 is touching the $i^{th}$ side, we compute if particle 1 will stay in the polygon or not. Then we generate the reachable set using all the vertices of the polygon and potential place of particle 1. We unify all the reachable sets corresponding to all the sides. Alg.~\ref{alg:polygonReachbale} computes reachable set for any convex polygonal workspace. 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets$ line with $(p_{i}', p_{i+1}')$
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(15,0){Case 1:$s_1$ does not hit boundary}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,0){Case 2:$s_1$ hits boundary}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(25,0){Generates polygon}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the reachable set when  one particle collides with edge $i,i+1$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}

>>>>

\begin{figure}
\centering
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionH.pdf}\end{overpic}
\begin{overpic}[width=0.47\columnwidth]{twoRobotRegionV.pdf}\end{overpic}
\caption{\label{fig:TwoRegions}
Boundary interaction is used to change the relative positions of the particles. Each particle gets the same control input. 
(left) If particle 2 hits the bottom wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and  particle 1 can move to anywhere in the shaded area. 
(right) Similarly, if particle 2 hits the right wall before particle 1 reaches a wall, particle 2 can reach anywhere along the green line, and then particle 1 can move to anywhere in the shaded area. 
}
\end{figure}
If a particle is touching a wall, the other particle can move freely in the reachable set as shown in Fig.~\ref{fig:TwoRegions}.
 We compute the reachable set for any convex workspace.
 Fig.~\ref{fig:polygonAlg} illustrates the procedure to construct the reachable set generated by collisions with the $i^{th}$ side. If one particle hist side $i$ before the other ($\overline{ s_1s_2 }\nparallel \overline{ p_i p_{i+1}} $), the reachable set is defined by a polygon, constructed in line 2-13 of Alg.~\ref{alg:polygonReachbale}. The union of these polygons for all $n$ sides is the reachable set of $\Delta$ configurations.
 % by computing the reachable set for all the sides of the polygon. Fig.~\ref{fig:polygonAlg} shows different cases with the particles and an arbitrary side. If particle 2 is touching the $i^{th}$ side, we compute if particle 1 will stay in the polygon or not. Then we generate the reachable set using all the vertices of the polygon and potential place of particle 1. We unify all the reachable sets corresponding to all the sides. Alg.~\ref{alg:polygonReachbale} computes reachable set for any convex polygonal workspace. 
 \begin{algorithm}[htb]
\caption{ { \sc ReachableSetPolygon}($s_1,s_2,g_1,g_2, P$)}\label{alg:polygonReachbale}
\begin{algorithmic}[1]
%\scriptsize
\Require knowledge of starting $(s_1,s_2)$ and goal $(g_1,g_2)$ positions of  two particles. 
$P$ is a list of the vertices of a convex polygon. %RSet contains all the reachable polygons.
\State $R_{\textrm{SET}\gets \{\}}$
\For {$p_i$ in $P$}
\State $p_{i}' \gets s_1 + s_2 - p_i$
\State $p_{i+1}' \gets s_1 + s_2 - p_{i+1}$
\State $L \gets$ line with $(p_{i}', p_{i+1}')$
\State $l_i, l_{i+1} \gets $ intersections of $L$ and polygon $P$
\If {$p_{i}'$ not inside polygon $P$}
\State $p_{i}' \gets l_i$
\EndIf
\If {$p_{i+1}'$ not inside polygon $P$}
\State $p_{i+1}' \gets l_{i+1}$
\EndIf
%\State $D \gets$ All vertices $\in [ l_i , l_{i+1} ] $
\State $D \gets$ $s_2 - s_1 -([l_i, v_{\textrm{min}}, ..., p_i ] -p_i' $,

@@

\begin{figure*}
\centering
\renewcommand{\figwid}{0.66\columnwidth}
\begin{overpic}[width =\figwid]{anypolygon1.pdf}\put(15,0){\tiny{Case 1: $s_1$ does not hit boundary}}\put(28,39){$s_2$}\put(63,50){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon2.pdf}\put(25,0){\tiny{Case 2: $s_1$ hits boundary}}\put(20,40){$s_2$}\put(55,58){$s_1$}
\end{overpic}
\begin{overpic}[width =\figwid]{anypolygon3.pdf}\put(25,0){\tiny{Generates polygon defined by $\overline{ p_i p_{i+1}}$ }}
\end{overpic}
\caption{\label{fig:polygonAlg}{ Steps to generate  the reachable set when  one particle collides with edge $i,i+1$ of a convex polygonal workspace.}
\vspace{-1em}
}
\end{figure*}
